---
title: "Who Does More Pushups"
author: "Adesuwa Mukoro"
date: "Fall 2020"
output:
html_document:
number_sections: true
toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
data(pushups)
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
pushups is a numerical variable
position is categorical
we will load the numerical~cat template

$H_0$:The null hypothesis states that there is no difference in the in the average number of pushups players can do in two minutes based on the position they play

$H_A$:The alternative hypothesis states that there is a difference in the average number of pushups players can do in two minutes based on the position they play
# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
plot(pushups~position,data=pushups)
```

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(pushups~position,data=pushups)
```
## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=pushups)
```
# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
we use a t test because the categorical variable has only two levels of position line and skill
The null hypothesis shows a difference in the number of pushups between line and skill.Skill has a significant number of pushups more than line

The p-value is 0.0000094 < 0.05. we reject the null hypothesis. we conclude that the number of pushups done in two minutes depends upon position. On average, the skill players do about 3 times as many pushups in two minutes as the line players